Spfy: distributed predictive genomics of E.coli with graph based result linkage

### 2017-08-17 paper-webserver.tex
CHANGE: the functionality para should only cover the analysis modules, not data storage

\section{FUNCTIONALITY}

% Describe available functions in spfy
% para covering everything
Spfy performs reference laboratory tasks: O-antigen and H-antigen typing, Shiga-toxin (STX) typing,  virulence factor (VF) and antimicrobial resistance (AMR) gene determination, and related strain determination.
Spfy also performs bioinformatics analyses: pangenome generation, statistical significance testing of genome markers for user-defined groups, and AMR predictions using support vector machines (SVMs).

@@

% storage of results
The results from ECTyper, RGI, Phylotyper, and Panseq are converted into a graph structure and linked the the genomes they originated from.

% use of stored results
By retrieving results from the database, Spfy provides group comparisons using Fishers, and can build SVMs to predict AMR based off of the presence of particular pangenome regions.

>>>>

\section{FUNCTIONALITY}
% ONLY FOCUS ON THE ANALYSIS MODULES
% Describe available functions in spfy
% para covering everything
Spfy performs reference laboratory tasks: O-antigen and H-antigen typing, Shiga-toxin (STX) typing,  virulence factor (VF) and antimicrobial resistance (AMR) gene determination, and related strain determination.
Spfy also performs bioinformatics analyses: pangenome generation, statistical significance testing of genome markers for user-defined groups, and AMR predictions using support vector machines (SVMs).

@@

% group comparisons
By retrieving results from the database, Spfy provides group comparisons using Fishers.
...

% Panpredic???
